---
title: "Churn Prediction"
author: "Yaswanth Kumar Reddy"
date: "May 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Statement

In telecom domain where the customer acquisition has higher cost than customer retention and where there is a rampant price war, it becomes important to predict and profile the customer behavior and predict them so that offers can be rolled out to retain them prior to switching.
 
Data consist of the various behavior of customers and the last column states if the customer is still with the existing telecom company or not.

## Objective

1. Understand factors contributing to customer churn.
2. Build a churn prediction model.
3. Model evaluation.
4. What can be done to restrict customers from churning.

```{r eval=FALSE, echo=FALSE}
setwd("D:/Users/1015624/GE Internal/My Docs/Work/Telecom")
```

```{r eval=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
```

## Data Overview

Read the data

```{r}
dat <- read.csv("data.csv")
```

Looking at the summary of the data. *Churn* is our target variable.

```{r eval=FALSE}
summary(dat)
head(dat)
```

From the summary of the data it is observed that there are no missing values. For a confirmation we shall check again if there are any NAs in each column .

```{r}
colSums(is.na(dat))
```

```{r}
dim(dat)
```

The distribution of target variable is more or less fine .

```{r}
prop.table(table(dat$Churn))
```

## Data Cleaning/Data Preprocessing


```{r}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
